Draft1

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Added histogram and brief description of data

@@

@@

To examine the specific effect of the Way of Teaching on the rate of entrepreneurship we decided to select the following dependent, control, and explanatory variables.

@@

As a reference, we can show the distribution of our explanatory variable "Way of Teaching" in the following histogram.

```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}

# Library required packages
library(ggvis)
library(devtools)
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(shiny)
library(httpuv)

# Create a vector of packages used
pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
          'stargazer', 'Amelia')

# Import WayofTeaching data
wot <- repmis::source_data()

ggvis(wot, props(x= ))

ggvis(faithful, props(x = ~eruptions, fill := "#fff8dc")) +
  layer_histogram(binwidth = 0.25) +
  guide_axis("x", title = "eruptions") +
  guide_axis("y", title = "count")

@@

In order to trace specifically how supportive of one's self-confidence a given education system is, we chose to use one specific item of the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection) as a proxy, namely D01.

"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"

##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship

We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention. We will study each of these successively as we may well observe different effects.

To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:

- Established Business Ownership Rate (Percentage) 
- Nascent Entrepreneurship Rate (Percentage)
- Entrepreneurial intention Rate (Percentage)

##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System

As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem. To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence. First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business. Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur. Both of these data sets indicate the average percentage for each characteristic at the country-level.

##### Regressions

The following equations were used to determine the relationship between our dependent and explanatory variables:

1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$

2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$

3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$

The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey. PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."

#### Data Collection and Cleaning

To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.

**Necessary R Packages**

The following packages were needed to complete the data collection portion of this assignment:

- repmis  
- tidyr  
- reshape  
- plyr  
- WDI

**GEM Data**

GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program. To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).  We then linked to the RAW version of the files and added the code required to load them from *R*.  The repmis package is required to load these documents from the repository.

Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.  In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name). This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.

For all 33 OECD countries we should have 13 observations, one per year from 2001 to 2013, for each variable. However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.

>>>>

```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}

# Library required packages
library(ggvis)
library(devtools)
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(shiny)
library(httpuv)
library(ggplot2)

# Create a vector of packages used
pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
          'stargazer', 'Amelia', 'ggplot2')

# Import WayofTeaching data
wot <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")

@@

The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.

@@

To understand the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.

@@

Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.  To illustrate the distribution of this data, we have created the following histogram.  As shown in the histogram, the largest density of scores is approximately 2.3, which lies between the "somewhat false" and "neither true or false" categories.  This is not a whole number because the scores given by each of the 4 experts surveyed for each frameork condition are averaged to create a national-level number.  As discussed later in this paper, this presents some difficulties in drawing substantive conclusions from this data.  Namely, a large number of indifferent responses complicate the process of determining the influence we would like to analyze.

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}

# Create a histogram showing the distribution of Way of Teaching
qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)

@@

Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).  These three regression equations are as follows:

1. $PercentEntreIntention = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$

2. $PercentNascent = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$

3. $PercentOwner = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$

The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities
